Simulations of Ballot Polling Risk-Limiting Audits

### 2022-10-08 providence/sections/workload.tex
workload

Importantly, this gives us a way to estimate the expected cost, as well as which round schedule value $p$ achieves it, for arbitrary round cost. For each round cost $c_r$, we estimate the minimum of the data like that shown in Figure~\ref{fig:with_round_cost} by fitting a lower order polynomial.
Figure~\ref{fig:optimal_costs} shows the optimal achievable workload for a wide range of per round costs. Figure~\ref{fig:optimal_ps} shows the corresponding round schedule parameters $p$ that achieve the minimal workloads. For any reasonable round costs, Providence minimizes cost with at least roughly $10\%$ and $30\%$ improvement over SO BRAVO and EoR BRAVO respectively.

>>>>

Importantly, this gives us a way to estimate the expected cost, as well as which round schedule value $p$ achieves it, for arbitrary round cost. For each round cost $c_r$, we produce a dataset analagous to that of Figure~\ref{fig:with_round_cost} and then find the minimum average cost achieved for each of the audits and its corresponding stopping probability $p$. 
Figure~\ref{fig:optimal_costs} shows the optimal achievable workload for a wide range of per round costs. For very low round costs, the workload function approaches just the total number of ballots, and so, as seen in Figure~\ref{fig:abv_bals}, the three approaches differ by less. On the other hand, for extremely larger values of round cost, the average number of ballots has little impact on the workload function, and so the three audits again have similar values. For more reasonable values of the round cost $c_r$, SO BRAVO and EoR BRAVO achieve minimum cost roughly $1.1$ and $1.3$ times greater than that of Providence.
Figure~\ref{fig:optimal_ps} shows the corresponding round schedule parameters $p$ that achieve these minimal workloads. As expected, a overhead for each round means that larger round sizes are needed to achieve an optimal audit, and so for all three audit $p$ increases as a function of $c_r$. Notice that Providence is generally above and to the left of SO BRAVO, and SO BRAVO is generally above and to the left of EOR BRAVO. This relationship reflects the fact that for the same round cost, Providence can get away with a larger stopping probability because it requires fewer ballots.
